### 2018-02-09 submission/manuscript.Rmd
update methods

***Obtaining Genera Relative Abundance and Selected Models:***
For the genera analysis of the RR, OTUs were added together based on the genus or lowest available taxonomic classification level and the total average counts, for 100 different subsamplings, were collected. The OTU based Random Forest Models using selected OTUs utilized a similar approach except that the OTUs were not aggregated together by taxonomic identity but kept as separate OTUs. OTU Random Forest models using the full community included all OTUs while those for the selected model included only those OTUs that had a taxonomic classification to a variable in the top 5 increased of top 5 decreased OR based on P-value.

@@

***Assessing Important Random Forest Model Variables:***
Using Mean Decrease in Accuracy (MDA) the top 10 most important variables to the Random Forest model were obtained in two different ways depending on whether the model used genera or OTU data. For the genus based models, the number of times that a genus showed up in the top 10 of the training set across each study was counted while, for the OTU based models, the medians for each OTU across 100 different 80/20 splits of the data was generated and the top 10 OTUs then counted for each study. Common taxa, for the OTU based models, were identified by using the lowest classification within the RDP database for each of the specific OTUs obtained from the previous counts and the number of times this classification occurred in the top 10, in each study, was recorded. The two studies that had adenoma tissue were equally divided between matched and unmatched groups and were grouped together for the counting of the top 10 genera and OTUs.

>>>>

***Obtaining Genera Relative Abundance and Selected Models:***
For the genera analysis of the OR, OTUs were added together based on the genus or lowest available taxonomic classification level and the total average counts, for 100 different subsamplings. The select models for the first approach utilized the top 5 most significantly increased and decreased ORs. For this approach, the full community models ufor each study were built by utilizing all genera and lowest taxnomic groups identified within that particular study. The select models for the second approach, that used OTU-based Random Forest models, utilized a similar method as the first approach. The main difference was that any OTU that taxonomically classified to one of the genera in the top 5 increased or decreased OR were included in the select model. OTU Random Forest models using the full community included all OTUs.

@@

***Assessing Important Random Forest Model Variables:***
Using Mean Decrease in Accuracy (MDA) the top 10 most important variables to the Random Forest model were obtained for the full models of the two different approaches used. For the first approach utilizing genus-based models, the number of times that a genus showed up in the top 10 of the training set across each study was counted. For the second approach, that utilized the OTU-based models, the medians for each OTU across 100 different 80/20 splits of the data was generated and the top 10 OTUs then counted for each study. Common taxa, for the OTU based models, were identified by using the lowest classification within the RDP database for each of the specific OTUs obtained from the previous counts and the number of times this classification occurred in the top 10, in each study, was recorded. Finally, for the two studies that had adenoma tissue (Lu and Flemer) were equally divided between matched and unmatched studies and were grouped together for the counting of the top 10 genera and OTUs.

### 2018-02-09 submission/manuscript.tex
update methods

\textbf{\emph{Obtaining Genera Relative Abundance and Selected Models:}}
For the genera analysis of the RR, OTUs were added together based on the
genus or lowest available taxonomic classification level and the total
average counts, for 100 different subsamplings, were collected. The OTU
based Random Forest Models using selected OTUs utilized a similar
approach except that the OTUs were not aggregated together by taxonomic
identity but kept as separate OTUs. OTU Random Forest models using the
full community included all OTUs while those for the selected model
included only those OTUs that had a taxonomic classification to a
variable in the top 5 increased of top 5 decreased OR based on P-value.

@@

\textbf{\emph{Assessing Important Random Forest Model Variables:}} Using
Mean Decrease in Accuracy (MDA) the top 10 most important variables to
the Random Forest model were obtained in two different ways depending on
whether the model used genera or OTU data. For the genus based models,
the number of times that a genus showed up in the top 10 of the training
set across each study was counted while, for the OTU based models, the
medians for each OTU across 100 different 80/20 splits of the data was
generated and the top 10 OTUs then counted for each study. Common taxa,
for the OTU based models, were identified by using the lowest
classification within the RDP database for each of the specific OTUs
obtained from the previous counts and the number of times this
classification occurred in the top 10, in each study, was recorded. The
two studies that had adenoma tissue were equally divided between matched
and unmatched groups and were grouped together for the counting of the
top 10 genera and OTUs.

>>>>

\textbf{\emph{Obtaining Genera Relative Abundance and Selected Models:}}
For the genera analysis of the OR, OTUs were added together based on the
genus or lowest available taxonomic classification level and the total
average counts, for 100 different subsamplings. The select models for
the first approach utilized the top 5 most significantly increased and
decreased ORs. For this approach, the full community models ufor each
study were built by utilizing all genera and lowest taxnomic groups
identified within that particular study. The select models for the
second approach, that used OTU-based Random Forest models, utilized a
similar method as the first approach. The main difference was that any
OTU that taxonomically classified to one of the genera in the top 5
increased or decreased OR were included in the select model. OTU Random
Forest models using the full community included all OTUs.

@@

\textbf{\emph{Assessing Important Random Forest Model Variables:}} Using
Mean Decrease in Accuracy (MDA) the top 10 most important variables to
the Random Forest model were obtained for the full models of the two
different approaches used. For the first approach utilizing genus-based
models, the number of times that a genus showed up in the top 10 of the
training set across each study was counted. For the second approach,
that utilized the OTU-based models, the medians for each OTU across 100
different 80/20 splits of the data was generated and the top 10 OTUs
then counted for each study. Common taxa, for the OTU based models, were
identified by using the lowest classification within the RDP database
for each of the specific OTUs obtained from the previous counts and the
number of times this classification occurred in the top 10, in each
study, was recorded. Finally, for the two studies that had adenoma
tissue (Lu and Flemer) were equally divided between matched and
unmatched studies and were grouped together for the counting of the top
10 genera and OTUs.
